%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

%---------------------------------------------------------
\cventry
{Freelance DevOps Consultant \& Automation Engineer} % Job title
{BNP PARIBAS, CIB division} % Organization
{Paris, France} % Location
{Dec. 2023 - Dec. 2024} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Role:} Member of the Observability \& Monitoring team.}
    \item {\textbf{Mission \& Context:} As part of the overhaul of the World Wide observability \& monitoring team around Dynatrace, I was involved as a consultant to advise on DevOps best practices applied to observability.}
    \item {\textbf{Environment:} Dynatrace, Ansible \& Ansible Tower, Python, Git, Jira, Jenkins, Artifactory, Service Now.}
    \item {Installation of Dynatrace agent on Linux and Windows servers, using Ansible for automation.}
    \item {Maintenance of the on-premise Dynatrace solution, Elasticsearch \& Cassandra. Setup of Backup \& Restoration of metric data. Implementation of backup \& restoration of configurations with Monaco (Monitoring As Code).}
    \item {Support for development teams in instrumenting applications for monitoring.}
    \item {Collaboration with World Wide team members to ensure effective performance monitoring and observability throughout the organization.}
    \item {Setup and maintenance of Dynatrace solutions for comprehensive application and infrastructure monitoring World Wide Europe/America/Asia.}
    \item {Advocacy for Git usage for version control, maintaining configuration files and scripts related to Dynatrace configurations.}
    \item {Advocacy for the use of Jira for project tracking to improve overall task and resource management. By integrating Jira into our project management processes, we were able to benefit from more accurate planning, transparent task tracking, and effective collaboration among team members. This recommendation optimized our workflows and ensured smoother project execution.}
    \item {Collaborative work to enhance overall observability strategies, ensuring a proactive approach to issue detection and resolution.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Freelance DevOps Consultant} % Job title
{Canal Plus. (Bolloré Group)} % Organization
{Paris, France} % Location
{Aug. 2023 - Dec. 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Role:} Platform DevOps Engineer}
    \item {\textbf{Mission \& Context:} As part of the Canal Plus entity, I was involved as a consultant for the maintenance and evolution of MediaHub, a cross-functional tool for group channel scheduling.}
    \item {\textbf{Environment:} Ansible, Git, Jenkins, Artifactory, SonarQube, Elastic \& Kibana, Jira, Service Now.}
    \item {As a DevOps engineer, I led the setup of new end-to-end CI/CD pipelines, adhering to best practices.}
    \item {Promotion of Git usage for version control, implementation and maintenance of CI/CD workflows for efficient deployment of solution code.}
    \item {Introduction of SonarQube for code quality analysis, enhancing the overall development process.}
    \item {Advocacy for CI/CD best practices, preaching the importance of automation and continuous integration throughout the development cycle.}
    \item {Key role in the migration of version control systems, leading the transition from Bitbucket to GitLab. Successful feasibility demonstration of CI/CD process migration from Jenkins to GitLab CI.}
    \item {Collaboration with cross-functional teams, using Jira for effective project management and issue tracking.}
    \item {Continuous optimization and streamlining of deployment processes, ensuring faster and more reliable software delivery.}
    \item {Contribution to the development and implementation of best practices for DevOps processes within the team and organization.}
    \item {Close work with different services to ensure a smooth transition to a hybrid cloud model, meeting unique business requirements and fostering collaboration between teams.}
  \end{cvitems}        
}

%---------------------------------------------------------
\cventry
{Site Reliability Engineer (SRE)} % Job title
{Adyoulike Inc.} % Organization
{Paris, France} % Location
{Feb. 2023 - Jun. 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Role:} SRE \& DevOps Engineer}
    \item {\textbf{Mission \& Context:} As part of a team reinforcement, I was involved as a Site Reliability Engineer to maintain and improve the reliability of critical systems.}
    \item {\textbf{Environment:} Apache Mesos, Docker, Hadoop, ScyllaDB, Apache Airflow, Jira, Google Kubernetes Engine (GKE), AWS, GCP, OVH.}
    \item {Management of a multi-cloud environment covering OVH, AWS, GCP, and on-premise infrastructure.}
    \item {Maintenance and optimization of performance and reliability of critical technologies, including Apache Mesos, Kafka, Docker, and Hadoop for big data processing.}
    \item {Successful implementation of ScyllaDB in place of MongoDB on Ubuntu 18.04, improving database efficiency and scalability.}
    \item {Leadership in the migration of Apache Airflow to Google Kubernetes Engine (GKE) on Google Cloud Platform (GCP), ensuring a smooth transition and enhanced orchestration capabilities.}
    \item {Collaboration with cross-functional teams to maintain and support existing systems, ensuring high availability and reliability in a complex multi-cloud architecture.}
    \item {Execution of migration strategy, addressing specific challenges of a multi-cloud environment and diversified technology stack.}
    \item {Contribution to the development of SRE best practices, focusing on reliability, scalability, and effective incident response.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Integration Engineer and Big Data Administrator} % Job title
{Société Générale} % Organization
{Paris, France} % Location
{Mar. 2020 - Sept. 2022} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Role:} Big Data Integration Engineer \& Hadoop Administrator \& DevOps Engineer}
    \item {\textbf{Mission \& Context:} As part of the Société Générale retail banking division, I was involved as a Big Data integration engineer to maintain and improve data processing systems. Accompanying the migration of legacy deployment practices to a modern Continuous Integration/Continuous Deployment (CI/CD) approach.}
    \item {\textbf{Environment:} Hadoop, HBase, Kafka, Ansible, Git, Jenkins, Artifactory, SonarQube, Elastic \& Kibana, Jira, Service Now.}
    \item {As an integration engineer in a Hadoop production environment, contributed to the design, deployment, and optimization of complex data processing systems.}
    \item {Use of Ansible and Git to automate and expedite delivery process, particularly in a high-risk business area focused on fraud detection.}
    \item {Maintenance of Kafka as event engine for real-time data streaming, enabling efficient communication and data flow within Hadoop ecosystem.}
    \item {Maintenance of HBase as NoSQL database, providing scalable and distributed storage for large volumes of data generated in fraud detection analytics context.}
    \item {Collegial leadership in the initial migration of legacy deployment practices to modern Continuous Integration/Continuous Deployment (CI/CD) approach.}
    \item {Advocacy for CI/CD practice integration to streamline and enhance software development cycle.}
    \item {Confrontation with challenges during CI/CD adoption process, including resolving dependencies of legacy systems, ensuring backward compatibility, and alignment with strict security and compliance requirements in fraud detection banking domain.}
    \item {Collaboration with cross-functional teams to address challenges, establish best practices, and ensure smooth transition to modern CI/CD builds.}
    \item {Contribution to development of robust CI/CD pipelines, integrating automated testing, deployment strategies, and version control to ensure reliability and efficiency of software releases.}
  \end{cvitems}  
}

%-------------------------------------------------------------------
\end{cventries}
