%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{DevOps Consultant} % Job title
{Digipulse Communication} % Organization
{Nice/Paris/Tunis, France/Tunisia} % Location
{Jan. 2024 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Mission \& Context:} As part of the company's digital transformation, I'm engaged in establishing it by adopting a Cloud-first approach across two cloud providers.}
    \item {\textbf{Environment:} AWS, Scaleway, Azure, Kubernetes, Docker, Jenkins, Git, Ansible, Terraform, Vault, Consul, Packer, Python, Bash, Trello.}
    \item {Implementation of a DevOps strategy to streamline and enhance development and deployment processes.}
    \item {Establishment of CI/CD pipelines to automate the deployment of applications and services.}
    \item {Utilization of Terraform \& CloudFormation for infrastructure management.}
  \end{cvitems}
}

%----------------
\cventry
{Freelance DevOps Consultant \& Automation Engineer} % Job title
{BNP PARIBAS, CIB division} % Organization
{Paris, France} % Location
{Dec. 2022 - Dec. 2023} % Date(s)
{
  \begin{cvitems}
    \item {\textbf{Mission \& Context:} As part of the revamp of the Worldwide observability \& monitoring team around Dynatrace, I was involved as a consultant to advise on DevOps best practices applied to observability.}
    \item {\textbf{Environment:} Dynatrace, Ansible \& Ansible Tower, Python, Git, Jira, Jenkins, Artifactory, ServiceNow.}
    \item {Installation of Dynatrace agent on Linux and Windows servers, using Ansible for automation.}
    \item {Maintenance of the Dynatrace, Elasticsearch \& Cassandra on-premise solution. Implementation of data metrics backup \& restoration. Implementation of configuration backup \& restoration with Monaco (Monitoring As Code).}
    \item {Support for development teams in instrumenting applications for monitoring.}
    \item {Collaboration with Worldwide team members to ensure effective performance monitoring and observability across the organization.}
    \item {Setup and maintenance of Dynatrace solutions for comprehensive application and infrastructure monitoring Worldwide Europe/Americas/Asia.}
    \item {Recommendation of using Git for version control, maintaining configuration files and scripts related to Dynatrace configurations.}
    \item {Recommendation of using Jira for project tracking to improve overall task and resource management.}
    \item {Collaborative work to enhance global observability strategies, ensuring a proactive approach to issue detection and resolution.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Freelance DevOps Consultant} % Job title
{Canal Plus (Bolloré Group)} % Organization
{Paris, France} % Location
{Aug. 2023 - Dec. 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Mission \& Context:} Within the Canal Plus entity, I was engaged as a consultant for the maintenance and evolution of MediaHub, a cross-channel scheduling tool for the group.}
    \item {\textbf{Environment:} Ansible, Git, Jenkins, Artifactory, SonarQube, Elastic \& Kibana, Jira, ServiceNow.}
    \item {As a DevOps engineer, led the end-to-end setup of new CI/CD pipelines, adhering to best practices.}
    \item {Advocated the use of Git for version control, implemented and maintained CI/CD workflows for efficient solution code deployment.}
    \item {Introduced SonarQube for code quality analysis, enhancing the entire development process.}
    \item {Promoted and advocated for CI/CD best practices, emphasizing automation and continuous integration throughout the development cycle.}
    \item {Key role in version control system migration, leading the transition from Bitbucket to GitLab. Successfully demonstrated feasibility for migrating Jenkins CI processes to GitLab CI.}
    \item {Collaborated with cross-functional teams, using Jira for effective project management and issue tracking.}
    \item {Continuously optimized and streamlined deployment processes, ensuring faster and more reliable software delivery.}
    \item {Contributed to the development and implementation of DevOps best practices within the team and organization.}
    \item {Worked closely with various departments to ensure a smooth transition to a hybrid cloud model, addressing unique business requirements and fostering collaboration between teams.}
  \end{cvitems}        
}

%---------------------------------------------------------
\cventry
{Site Reliability Engineer (SRE)} % Job title
{Adyoulike Inc.} % Organization
{Paris, France} % Location
{Feb. 2023 - June 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Mission \& Context:} As part of a team reinforcement, I was involved as a Site Reliability Engineer to maintain and enhance the reliability of critical systems.}
    \item {\textbf{Environment:} Apache Mesos, Docker, Hadoop, ScyllaDB, Apache Airflow, Jira, Google Kubernetes Engine (GKE), AWS, GCP, OVH.}
    \item {Managed a multi-cloud environment covering OVH, AWS, GCP, and an on-premise infrastructure.}
    \item {Maintenance and performance optimization of critical technologies including Apache Mesos, Kafka, Docker, and Hadoop for large-scale data processing.}
    \item {Successfully implemented ScyllaDB replacing MongoDB on Ubuntu 18.04, improving database efficiency and scalability.}
    \item {Led the migration of Apache Airflow to Google Kubernetes Engine (GKE) on Google Cloud Platform (GCP), ensuring a seamless transition and enhanced orchestration capabilities.}
    \item {Collaborated with cross-functional teams to maintain and support existing systems, ensuring high availability and reliability in a complex multi-cloud architecture.}
    \item {Executed a migration strategy, addressing specific challenges of a multi-cloud environment and diverse technology stack.}
    \item {Contributed to the development of SRE best practices, focusing on reliability, scalability, and effective incident response.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Integration Engineer and Big Data Administrator} % Job title
{Société Générale} % Organization
{Paris, France} % Location
{Mar. 2020 - Sept. 2022} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Mission \& Context:} Within Société Générale's retail banking division, I was involved as a Big Data integration engineer to maintain and enhance data processing systems. Supported the migration from legacy deployment practices to a modern Continuous Integration/Continuous Deployment (CI/CD) approach.}
    \item {\textbf{Environment:} Hadoop, HBase, Kafka, Ansible, Git, Jenkins, Artifactory, SonarQube, Elastic \& Kibana, Jira, ServiceNow.}
    \item {As an integration engineer in a Hadoop production environment, contributed to the design, deployment, and optimization of complex data processing systems.}
    \item {Utilized Ansible and Git to automate and expedite delivery processes, particularly in a high-risk business domain focused on fraud detection.}
    \item {Maintenance of Kafka as an event engine for real-time data streaming, enabling efficient communication and data flow within the Hadoop ecosystem.}
    \item {Maintenance of HBase as a NoSQL database, providing scalable and distributed storage for large volumes of data generated in the context of fraud detection analytics.}
    \item {Collegial leadership in the initial migration from legacy deployment practices to a modern Continuous Integration/Continuous Deployment (CI/CD) approach.}
    \item {Promoted CI/CD integration practices to streamline and enhance the software development lifecycle.}
    \item {Faced challenges during CI/CD adoption, including resolving dependencies from legacy systems, ensuring backward compatibility, and alignment with strict security and compliance requirements in the fraud detection domain.}
    \item {Collaborated with cross-functional teams to address challenges, establish best practices, and ensure a smooth transition to modern CI/CD builds.}
    \item {Contributed to the development of robust CI/CD pipelines, integrating automated testing, deployment strategies, and version control to ensure reliability and efficiency of software releases.}
  \end{cvitems}  
}

%---------------------------------------------------------
\cventry
{Infrastructure Engineer} % Job title
{BNP Paribas, BP2I division} % Organization
{Paris, France} % Location
{Jan. 2018 - Mar. 2019} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Mission \& Context:} Maintaining the Splunk on-premise solution for BNP Paribas' BP2I division.}
    \item {\textbf{Environment:} Red Hat, Splunk, Git, GitLab CI, Ansible, Bash, Python, Jira, ServiceNow.}
    \item {Setup of on-premise Splunk solutions for BNP Paribas and its BP2I division.}
    \item {Led the implementation of Git for code control from a CI perspective.}
    \item {Deployment and CI/CD testing using GitLab CI pipelines.}
    \item {Infrastructure deployment using Ansible, ensuring efficient and consistent deployment processes.}
    \item {Collaborated with cross-functional teams to design and deploy scalable and secure infrastructure.}
    \item {Utilized version control systems, particularly Git, to manage configuration files and infrastructure code.}
    \item {Worked on optimizing system performance, identifying and resolving infrastructure-related issues.}
    \item {Contributed to the development and implementation of best practices for infrastructure management.}
    \item {Collaborated with team members to enhance overall system observability and monitoring.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{System Administrator} % Job title
{Synalabs} % Organization
{Paris, France} % Location
{Sept. 2017 - Dec. 2017} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Role:} Systems Administrator, Operations Engineer}
    \item {\textbf{Mission \& Context:} Managed and administered web hosting systems for various clients at Synalabs.}
    \item {\textbf{Environment:} Web hosting, Apache, Nginx, MySQL, PostgreSQL, Jenkins, Ansible, Docker, Pfsense Firewall, SSL, Bash, Python.} 
    \item {Configuration, maintenance, and monitoring of web servers, including Apache and Nginx.}
    \item {Installation and management of databases, including MySQL and PostgreSQL, to ensure optimal performance of hosted websites.}
    \item {Implemented robust security measures, including firewall configuration, SSL certificate management, and proactive vulnerability monitoring.}
    \item {Automation of recurring tasks using custom scripts and automation tools on Rundeck \& Jenkins.}
    \item {Provided technical support to clients to resolve hosting-related issues, including connectivity, performance, and security problem resolution.}
    \item {Collaborated with development teams to ensure effective deployment and management of web applications.}
    \item {Established reliable data backup and recovery strategies in case of disasters.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{DevOps Engineer} % Job title
{Deveryware} % Organization
{Paris, France} % Location
{June 2016 - Aug. 2017} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Mission \& Context:} Maintained and improved Deveryware's geolocation infrastructure.}
    \item {\textbf{Environment:} Proxmox, GitLab CE, Jenkins, HashiCorp Vault, Consul, Terraform, Packer, Ansible, Docker, Python, Bash.}
    \item {Utilized fully open-source environment: Proxmox, GitLab CE, Jenkins.}
    \item {Implemented dual-factor authentication to enhance application security.}
    \item {Proactively maintained the geolocation solution, ensuring availability and reliability.}
    \item {Deployed and managed infrastructure using HashiCorp tools to ensure scalability and security.}
    \item {Worked closely with the team to establish DevOps best practices in project workflows.}
    \item {Integrated and optimized HashiCorp tools to enhance deployment and management processes.}
    \item {Contributed to continuous improvement of team practices and overall project efficiency.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Freelance Consultant System Engineer} % Job title
{AB Tasty} % Organization
{Paris, France} % Location
{Dec. 2015 - June 2016} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Mission \& Context:} Engaged as a consultant for AB Tasty's cloud infrastructure maintenance and evolution within an architectural mission.}
    \item {\textbf{Environment:} AWS, Docker, Ansible, Terraform, Packer, Jenkins, Git, Python, Bash.}
    \item {Deployed highly available web applications on AWS, using Docker for containerization.}
    \item {Automated infrastructure tasks using Ansible, Terraform, Packer, and Jenkins pipelines, ensuring efficient and consistent infrastructure management.}
    \item {Improved system security and resilience by implementing best practices and backup solutions.}
    \item {Worked closely with development teams to understand requirements and provide tailored infrastructure solutions.}
    \item {Actively participated in continuous improvement of team processes and practices.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Operations Engineer} % Job title
{Meetic} % Organization
{Paris, France} % Location
{Mar. 2015 - Dec. 2015} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Mission \& Context:} Maintained operational infrastructure for Meetic.}
    \item {\textbf{Environment:} Bare metal, VMware, Apache, Nginx, MySQL, PostgreSQL, Docker, Ansible, Git, Jira, Kafka, Bash, Python.}
    \item {Managed on-site infrastructure for Meetic, ensuring optimal performance and continuous reliability.}
    \item {Maintained and supported Meetic's solution infrastructure with continuous monitoring and proactive issue resolution.}
    \item {Active participation within the team to provide multi-environment solutions, adapting infrastructure to various operational needs.}
    \item {Collaborated closely with cross-functional teams to meet and satisfy infrastructure requirements.}
    \item {Utilized best practices to ensure scalability and security of infrastructure supporting Meetic services.}
    \item {Contributed to continuous improvement of infrastructure processes and operational efficiency.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Operations Technician} % Job title
{Ecritel} % Organization
{Paris, France} % Location
{Mar. 2012 - Mar. 2015} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Mission \& Context:} Outsourcing and management of enterprise platforms.}
    \item {\textbf{Environment:} Datacenter, VMware Cloud.}
    \item {Resolved level 1, 2, and 3 problems.}
    \item {Managed incidents and service requests.}
    \item {Managed backups and restorations.}
    \item {Managed updates and patches.}
    \item {24/7 on-call duty.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Operations Technician, Systems Administrator} % Job title
{Internet-fr} % Organization
{Paris, France} % Location
{Mar. 2011 - Mar. 2012} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Mission \& Context:} Outsourcing and management of enterprise platforms.}
    \item {\textbf{Environment:} Datacenter, VMware Cloud, Debian.}
    \item {Resolved level 1, 2, and 3 problems.}
    \item {Managed incidents and service requests.}
    \item {Managed backups and restorations.}
    \item {Managed updates and patches.}
    \item {24/7 on-call duty.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
